---
title: "SDS 315 HW 3"
subtitle: "https://github.com/sophiayang5/SDS-315-HW-3"
author: "Sophia Yang (sy23928)"
output:
  pdf_document:
    toc: true
    toc_depth: 5
    number_sections: false
date: "2025-02-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(mosaic)
library(ggplot2)
```

# Problem 1
```{r}
gas <- read.csv("gasprices.csv")
```


## Part A.

```{r}
# bootstrap the diffmean
boot_competition = do(10000)*diffmean(Price ~ Competitors, data = resample(gas))
# graph the difference in mean price according to whether or not there is competition
ggplot(boot_competition) + geom_histogram(aes(x = diffmean)) + 
  labs(
    title = "Comparing Prices between Gas Stations With and Without Competition",
    x = "Difference in Average Price",
    y = "Count"
  )
# find the confidence interval
confint(boot_competition, level = 0.95)
```

The claim was that gas stations charge more if they lack direct competition in sight. However, the bootstrapped histogram of the difference in means between gas stations with and without direct competition, as well as the 95% confidence interval, show that no difference is likely. More specifically, the difference in price between gas stations with and without direct competition is somewhere between -0.055 and 0.008 (which contains 0), with 95% confidence. Thus, the claim is not supported.


## Part B.

```{r}
# bootstrap the correlation coeff
boot_income = do(10000)*cor(Price ~ Income, data = resample(gas))
# graph the correlation of gas prices with the surrounding median household income
ggplot(boot_income) + geom_histogram(aes(x = cor)) +
  labs(
    title = "Correlation between Gas Station Prices and Household Income",
    x = "Correlation Coefficient",
    y = "Count"
  )
# find the confidence interval
confint(boot_income, level = 0.95)
```

The claim was that gas stations have higher gas prices when the surrounding median household income is higher. The bootstrapped histogram of the correlation coefficients between gas stations' prices and the surrounding median household income, as well as the 95% confidence interval, show that there is likely not much of a correlation between higher gas prices and household income. More specifically, the correlation coefficient in gas stations' prices and household income is somewhere between 0.120 and 0.569, with 95% confidence. Thus, the claim is not strongly supported.


## Part C.

```{r}
# bootstrap the diffmean
boot_stoplight = do(10000)*diffmean(Price ~ Stoplight, data = resample(gas))
# graph the difference in mean price according to whether or not the gas station is at a stoplight
ggplot(boot_stoplight) + geom_histogram(aes(x = diffmean)) + 
  labs(
    title = "Comparing Prices between Gas Stations At and Not At Stoplights",
    x = "Difference in Average Price",
    y = "Count"
  )
# find the confidence interval
confint(boot_stoplight, level = 0.95)
```

The claim was that gas stations at stoplights charge more than gas stations not at stoplights. However, the bootstrapped histogram of the difference in means between gas stations at and not at stoplights, as well as the 95% confidence interval, show that no difference is likely. More specifically, the difference in price between gas stations at and not at stoplights is somewhere between -0.039 and 0.030 (which contains 0), with 95% confidence. Thus, the claim is not supported.


## Part D.

```{r}
# bootstrap the diffmean
boot_highway = do(10000)*diffmean(Price ~ Highway, data = resample(gas))
# graph the difference in mean price according to whether or not the gas station has direct highway access
ggplot(boot_highway) + geom_histogram(aes(x = diffmean)) + 
  labs(
    title = "Prices between Gas Stations With and Without Highway Access",
    x = "Difference in Average Price",
    y = "Count"
  )
# find the confidence interval
confint(boot_highway, level = 0.95)
```

The claim was that gas stations with direct highway access charge more than gas stations without direct highway access. The bootstrapped histogram of the difference in means between gas stations with and without direct highway access, as well as the 95% confidence interval, show that a difference is likely. More specifically, the difference in price between gas stations with and without direct highway access is somewhere between 0.009 and 0.081 (which does not contain 0), with 95% confidence. Thus, the claim is supported.


## Part E.

```{r}
# make a non-Shell variable
gas_brand = gas |>
  mutate(Shell = ifelse(Brand == "Shell", yes = TRUE, no = FALSE))
# bootstrap the diffmean
boot_shell = do(10000)*diffmean(Price ~ Shell, data = resample(gas_brand))
# graph the difference in mean price according to whether or not the gas station is Shell
ggplot(boot_shell) + geom_histogram(aes(x = diffmean)) + 
  labs(
    title = "Prices between Shell Gas Stations and Non-Shell Stations",
    x = "Difference in Average Price",
    y = "Count"
  )
# find the confidence interval
confint(boot_shell, level = 0.95)
```

The claim was that Shell charges more than all other non-Shell brands. However, the bootstrapped histogram of the difference in means between Shell gas stations and non-Shell gas stations, as well as the 95% confidence interval, show that no difference is likely. More specifically, the difference in price between Shell gas stations and non-Shell gas stations is somewhere between -0.009 and 0.065 (which contains 0), with 95% confidence. Thus, the claim is not supported.


# Problem 2
```{r}
class <- read.csv("sclass.csv")
```

## Part A.

```{r}
# filter the dataset
class_AMG <- class |>
  filter(year == 2011, trim == "63 AMG")
# bootstrap the mean
boot_class_AMG = do(10000)*mean(~mileage, data = resample(class_AMG))
# graph the mean mileage 
ggplot(boot_class_AMG) + geom_histogram(aes(x = mean)) + 
  labs(
    title = "Average Prices for Used 2011 S-Class 63 AMGs",
    x = "Average Price",
    y = "Count"
  )
# find the confidence interval
confint(boot_class_AMG, level = 0.95)
```

The average mileage of 2011 S-Class 63 AMGs in the used-car market lies somewhere between $26,326.79 and $31,797.17, with 95% confidence.


## Part B.

```{r}
# filter the dataset
class_550 <- class |>
  filter(year == 2014, trim == "550") |>
  # make an isBlack variable
  mutate(isBlack = ifelse(color == "Black", yes = TRUE, no = FALSE))
# bootstrap the proportion
boot_class_550 = do(10000)*prop(~isBlack, data = resample(class_550))
# graph the proportion of black cars
ggplot(boot_class_550) + geom_histogram(aes(x = prop_TRUE)) +
  labs(
    title = "Proportion of Black 2014 S-Class 550s",
    x = "Proportion",
    y = "Count"
  )
# find the confidence interval
confint(boot_class_550, level = 0.95)
```

The proportion of black 2014 S-Class 550s in the used-car market lies somewhere between 0.417 and 0.453, with 95% confidence.


# Problem 3
```{r}
nbc <- read.csv("nbc_pilotsurvey.csv")
```


## Part A.

```{r}
# filter the dataset
nbc_person <- nbc |>
  filter(Show == "Living with Ed" | Show == "My Name is Earl")
# boostrap the diffmean
boot_nbc_person = do(10000)*diffmean(Q1_Happy ~ Show, data = resample(nbc_person))
# graph the difference in mean happiness according to the show
ggplot(boot_nbc_person) + geom_histogram(aes(x = diffmean)) + 
  labs(
    title = "Viewers' Happiness between \"Living with Ed\" and \"My Name is Earl\" ",
    x = "Difference in Viewers' Happiness",
    y = "Count"
  )
# find the confidence interval
confint(boot_nbc_person, level = 0.95)
```

The question was whether "Living with Ed" or "My Name is Earl" consistently produces a higher mean Q1_Happy response (on a scale of 1-5, with 5 being very happy) among viewers. I used a difference in mean bootstrap as well as a 95% confidence interval for the difference in means to answer this question. Both the bootstrapped histogram and the confidence interval show that no difference is likely. More specifically, the difference in Q1_Happy response between "Living with Ed" and "My Name is Earl" is somewhere between -0.400 and 0.106 (which contains 0), with 95% confidence. Thus, the claim is not supported: between the two shows, one of them does not consistently produce a higher mean Q1_Happy response among viewers at the 95% confidence level.


## Part B.

```{r}
# filter the dataset
nbc_annoyed <- nbc |>
  filter(Show == "The Biggest Loser" | Show == "The Apprentice: Los Angeles")
# boostrap the diffmean
boot_nbc_annoyed = do(10000)*diffmean(Q1_Annoyed ~ Show, data = resample(nbc_annoyed))
# graph the difference in mean annoyance according to the show
ggplot(boot_nbc_annoyed) + geom_histogram(aes(x = diffmean)) + 
  labs(
    title = "Annoyance between \"The Biggest Loser\" and \"The Apprentice: LA\" ",
    x = "Difference in Viewers' Annoyedness",
    y = "Count"
  )
# find the confidence interval
confint(boot_nbc_annoyed, level = 0.95)
```

The question was whether "The Biggest Loser" or "The Apprentice: Los Angeles" consistently produces a higher mean Q1_Annoyed (on a scale of 1-5, with 5 being very annoyed) response among viewers. I used a difference in mean bootstrap as well as a 95% confidence interval for the difference in means to answer this question. Both the bootstrapped histogram and the confidence interval show that a difference is likely. More specifically, the difference in Q1_Annoyed response between "The Biggest Loser" and "The Apprentice: Los Angeles" is somewhere between -0.524 and -0.026 (which does not contain 0), with 95% confidence. Thus, the claim is supported: between the two shows, one of them consistently produces a higher mean Q1_Annoyed response among viewers at the 95% confidence level.


## Part C.

```{r}
# filter the dataset
nbc_dancing <- nbc |>
  filter(Show == "Dancing with the Stars") |>
  # make a 4 or higher variable
  mutate(Very_Confused = ifelse(Q2_Confusing >= 4, yes = TRUE, no = FALSE))
# bootstrap the proportion
boot_nbc_dancing = do(10000)*prop(~Very_Confused, data = resample(nbc_dancing))
# graph the proportion of responses of 4 or greater
ggplot(boot_nbc_dancing) + geom_histogram(aes(x = prop_TRUE)) +
  labs(
    title = "Proportion of Confused \"Dancing with the Stars\" Viewers",
    x = "Proportion",
    y = "Count"
  )
# find the confidence interval
confint(boot_class_550, level = 0.95)
```

The question was what proportion of American TV watchers would we expect to give a response of 4 or greater to the Q2_Confusing question (on a scale of 1-5, with 5 being very confused) for "Dancing with the Stars." I used a proportion bootstrap as well as a 95% confidence interval for the proportion of responses that are 4 or greater to this question. The proportion of 4 or greater responses to the Q2_Confusing for "Dancing with the Stars" is somewhere between 0.417 and 0.453, with 95% confidence. Thus, we are 95% confident that the proportion of American TV watchers with those responses would lie within that range.


# Problem 4

```{r}
ebay <- read.csv("ebay.csv")

# create a ratio variable
ebay_ratio <- ebay |>
  mutate(revenue_ratio = rev_after/rev_before)
# bootstrap the diffmean
boot_ebay_ratio = do(10000)*diffmean(revenue_ratio ~ adwords_pause, data = resample(ebay_ratio))
# graph the difference in revenue ratio according to whether or not Ebay paid
ggplot(boot_ebay_ratio) + geom_histogram(aes(x = diffmean)) + 
  labs(
    title = "Revenue Ratio Between Paid and Non-Paid Google Search Ads",
    x = "Difference in Ebay's Revenue Ratio",
    y = "Count"
  )
# find the confidence interval
confint(boot_ebay_ratio, level = 0.95)
```

The question was whether or not paid search advertising on Google creates extra revenue for Ebay. I used a difference in mean bootstrap as well as a 95% confidence interval for the difference in means to answer this question. Both the bootstrapped histogram and the confidence interval show that a difference is likely. More specifically, the difference in the revenue ratios between paid search and non-paid search is somewhere between -0.091 and -0.013 (which does not contain 0), with 95% confidence. Thus, paid search advertising on Google likely creates extra revenue for Ebay at the 95% confidence level. 